Turbulence in compact to giant HII regions

### 2022-06-29 Corr.tex
Improve formatting of Table 4

\begin{table*}
\begin{center}
\caption{Linear regressions values in the form Y = aX + b between our turbulent parameters obtained using the chi-square statistic and properties of each region (Table \ref{tab:regions-properties}). The fifth column, $r$, is the Pearson correlation coefficient and the last column is the $p$-value. This results were obtained using the procedure in \citet{2007ApJ...665.1489K}.}
\begin{tabular}{cccccc}
\hline
            $Y$ &                   $X$ &                 $a$ &                 $b$ &       $r$ &      $p$ \\
\hline
    log $r_0$ &       log $S$ &   0.95 $\pm$ 0.33 &  -1.68 $\pm$ 0.71 &   0.86 &  0.003 \\
 log $\sigma$ &      log L(H) &   0.26 $\pm$ 0.11 &  -9.19 $\pm$ 4.33 &   0.86 &  0.003 \\
 log $\sigma$ &       log $S$ &   0.24 $\pm$ 0.17 &   0.24 $\pm$ 0.38 &   0.64 &   0.06 \\
 log $\sigma$ &   log $r_{0}$ &   0.18 $\pm$ 0.17 &   0.69 $\pm$ 0.12 &   0.51 &  0.164 \\
      log $m$ &      log Dist &  -0.02 $\pm$ 0.04 &   0.04 $\pm$ 0.08 &   -0.4 &   0.29 \\
      log $m$ &  log $\sigma$ &  -0.18 $\pm$ 1.03 &   0.14 $\pm$ 0.74 &  -0.37 &  0.327 \\
      log $m$ &   log $r_{0}$ &  -0.02 $\pm$ 0.07 &   0.01 $\pm$ 0.05 &  -0.28 &  0.469 \\
\bottomrule
\end{tabular}\label{tab:RestStats}
\end{center}
\end{table*}

@@

>>>>

\begin{table*}
\begin{center}
\caption{Linear regressions values in the form Y = aX + b between our turbulent parameters obtained using the chi-square statistic and properties of each region (Table \ref{tab:regions-properties}). The fifth column, $r$, is the Pearson correlation coefficient and the last column is the $p$-value. This results were obtained using the procedure in \citet{2007ApJ...665.1489K}.}
\begin{tabular}{RRRRRR}
  \toprule
  Y &                   X &                 a &                 b &       r &      p \\
  \midrule
  \log r_0 &         \log D_{\hii} &   0.94 \pm 0.33 &  -1.66 \pm 0.72 &   0.86 &  \mathbf{0.003} \\
  \log \sigma\pos &        \log L(\ha) &    0.28 \pm 0.10 &  -9.86 \pm 3.71 &   0.86 &  \mathbf{0.003} \\
  \sigma\pos &  \sigma_{\text{los}} &   1.03 \pm 0.44 &   7.35 \pm 2.83 &   0.78 &   \mathbf{0.010} \\[\smallskipamount]
  \log \sigma\pos &         \log D_{\hii} &   0.26 \pm 0.18 &   0.19 \pm 0.39 &   0.64 &   0.060 \\
  \log m &        \log d &  -0.02 \pm 0.04 &   0.04 \pm 0.08 &   -0.40 &   0.290 \\
  \sigma\pos &         r_{0} &    0.40 \pm 0.69 &   4.61 \pm 3.25 &   0.37 &  0.329 \\
  m &        \sigma\pos &  -0.01 \pm 0.03 &   1.12 \pm 0.21 &  -0.37 &  0.331 \\
  m &         r_{0} &   0.02 \pm 0.03 &   0.96 \pm  0.16 &  -0.09 &  0.824 \\
  \bottomrule
\end{tabular}\label{tab:RestStats}
\end{center}
\end{table*}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: strucfunc_paper
%%% End:
